### 2018-04-19 experiments.tex
now too long, needs trim

>>>>

In order to evaluate our approach and implementation, we applied
nondeterminism detection to three real world examples.  The primary
points we wanted to explore were (1) whether lightweight, automatic,
nondeterminism detection was able to reliably detect actual
nondeterminism (2) whether the overhead of nondeterminism
detection for real systems was acceptable and (3) the performance of
delta-debugging for real nondeterministic predicates.
